Beyond Adaptive Web Design

### 2014-02-19 paper/paper.tex
fix(paper): fix author
refactor(): extend Adaptive Input methods
refactor(): extend Evaluation and experiments

\title{Beyond Adaptive Web Design}
\titlerunning{Beyond Adaptive Web Design}
\author{Ján}{Antala}
\author{Michal}{Čerňanský}
\supervision{\ms}
            {\infosys}
            {~Assoc.~Professor}
            {\iai, \fiit}
\mail{hello@janantala.com}
\field{Web Science and Web Engineering}

@@

As we have many types of devices with web access we also have to adapt input methods for them. It is not just about screen sizes, but many displays also have touch capabilities.

@@

There have been made series of experiments on both adaptive input methods and web components. The goal has been to create reusable modules and components every developer can include into their web application. All of them have been released as open source and are available on GitHub.

>>>>

\title{Beyond Adaptive Web Design}
\titlerunning{Beyond Adaptive Web Design}
\author{Ján}{Antala}
\supervision{\ms}
            {\infosys}
            {~Assoc.~Professor Michal Čerňanský}
            {\iai, \fiit}
\mail{hello@janantala.com}
\field{Web Science and Web Engineering}

@@

As we have many types of devices with web access we also have to adapt input methods for them. It is not just about screen sizes, but many displays also have touch capabilities, are equiped with microphone, accelerometer, gyroscope or camera.

@@

There have been made series of experiments on both adaptive input methods and web components. To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects. All of them have been released as open source and are available on GitHub.
